Figures

### 2018-11-19 Analysis/Figures_in_R.Rmd
updated figures plots

>>>>

## Figure methods

```{r}
set.seed(42)
## Creating a 5 trait space
iris_rand <- cbind(iris[seq(from = 1, to = 150, by = 5), 1:4], rnorm(30))

## Plotting the 5 traits
pdf(file = "../Writing/Figures/figure_methods_biplot.pdf", width = 5, height = 5)
plot(iris_rand, pch = 19, xaxt = "n", yaxt = "n")
dev.off()

## Making a distance matrix
iris_dist <- dist(iris_rand)

## Making it 2D
pdf(file = "../Writing/Figures/figure_methods_2dPCO.pdf", width = 5, height = 5)
plot(cmdscale(iris_dist, k = 2), pch = 19, xaxt = "n", yaxt = "n", ylab = "", xlab = "")
dev.off()

## Making a PCA
pca <- princomp(iris_rand)$scores
pdf(file = "../Writing/Figures/figure_methods_PCA1.pdf", width = 5, height = 5)
plot(pca[,1:2], pch = 19, xaxt = "n", yaxt = "n", ylab = "", xlab = "")
dev.off()
pdf(file = "../Writing/Figures/figure_methods_PCA2.pdf", width = 5, height = 5)
plot(pca[,3:4], pch = 19, xaxt = "n", yaxt = "n", ylab = "", xlab = "")
dev.off()
pdf(file = "../Writing/Figures/figure_methods_PCA3.pdf", width = 5, height = 5)
plot(pca[,c(5,1)], pch = 19, xaxt = "n", yaxt = "n", ylab = "", xlab = "")
dev.off()
```
